\bibliography{references}

\begin{thebibliography}{10}

\bibitem{nazeri2019edgeconnect}
K. Nazeri, E. Ng, T. Joseph, F. Qureshi, and M. Ebrahimi.  
EdgeConnect: Generative image inpainting with adversarial edge learning.  
\textit{arXiv preprint arXiv:1901.00212}, 2019.

\bibitem{liu2015deep}
Z. Liu, P. Luo, X. Wang, and X. Tang.  
Deep learning face attributes in the wild.  
In \textit{International Conference on Computer Vision (ICCV)}, 2015.

\bibitem{goodfellow2014generative}
I. Goodfellow, J. Pouget-Abadie, M. Mirza, B. Xu, D. Warde-Farley, S. Ozair, A. Courville, and Y. Bengio.  
Generative adversarial networks.  
\textit{arXiv preprint arXiv:1406.2661}, 2014.

\bibitem{pathak2016context}
D. Pathak, P. Krahenbuhl, J. Donahue, T. Darrell, and A. A. Efros.  
Context encoders: Feature learning by inpainting.  
In \textit{CVPR}, pages 2536–2544, 2016.

\bibitem{darabi2012image}
S. Darabi, E. Shechtman, C. Barnes, D. B. Goldman, and P. Sen.  
Image melding: Combining inconsistent images using patch-based synthesis.  
\textit{ACM TOG}, 31(4):82–1, 2012.

\bibitem{liu2018partial}
G. Liu, F. A. Reda, K. J. Shih, T. C. Wang, A. Tao, and B. Catanzaro.  
Image inpainting for irregular holes using partial convolutions.  
In \textit{ECCV}, pages 85--100, 2018.

\bibitem{yu2019free}
J. Yu, Z. Lin, J. Yang, X. Shen, X. Lu, and T. S. Huang.  
Free-form image inpainting with gated convolution.  
In \textit{ICCV}, pages 4471--4480, 2019.

\bibitem{yu2018generative}
J. Yu, Z. Lin, J. Yang, X. Shen, X. Lu, and T. S. Huang.  
Generative image inpainting with contextual attention.  
In \textit{CVPR}, pages 5505--5514, 2018.

\bibitem{zhao2021comodgan}
S. Zhao, Z. Liu, Z. Lin, J.-Y. Zhu, and W. Xu.  
CoModGAN: Co-modulated generative adversarial networks.  
In \textit{NeurIPS}, 34:4439--4452, 2021.

\bibitem{johnson2016perceptual}
J. Johnson, A. Alahi, and L. Fei-Fei.  
Perceptual losses for real-time style transfer and super-resolution.  
In \textit{ECCV}, pages 694–711. Springer, 2016.

\bibitem{gatys2016image}
L. A. Gatys, A. S. Ecker, and M. Bethge.  
Image style transfer using convolutional neural networks.  
In \textit{CVPR}, pages 2414–2423, 2016.

\bibitem{gulrajani2017improved}
I. Gulrajani, F. Ahmed, M. Arjovsky, V. Dumoulin, and A. Courville.  
Improved training of Wasserstein GANs.  
In \textit{NeurIPS}, pages 5767–5777, 2017.

\bibitem{zhang2018unreasonable}
R. Zhang, P. Isola, A. A. Efros, E. Shechtman, and O. Wang.  
The unreasonable effectiveness of deep features as a perceptual metric.  
In \textit{CVPR}, pages 586–595, 2018.

\bibitem{wang2004image}
Z. Wang, A. C. Bovik, H. R. Sheikh, and E. P. Simoncelli.  
Image quality assessment: From error visibility to structural similarity.  
\textit{IEEE TIP}, 13(4):600–612, 2004.

\bibitem{hertz2023any}
B. Xia, Y. Zhang, S. Wang, Y. Wang, X. Wu, Y. Tian, W. Yang, and L. Van Gool.  
DiffIR: Efficient diffusion model for image restoration.  
\textit{arXiv preprint arXiv:2308.07950}, 2023.

\bibitem{bertalmio2000image}
M. Bertalmio, G. Sapiro, V. Caselles, and C. Ballester.  
Image inpainting.  
In \textit{Proc. SIGGRAPH}, pages 417–424, 2000.

\bibitem{criminisi2004region}
A. Criminisi, P. Perez, and K. Toyama.  
Region filling and object removal by exemplar-based image inpainting.  
\textit{IEEE TIP}, 13(9):1200–1212, 2004.

\bibitem{yi2020contextual}
L. Yi, Y. Liu, Y. Luo, Y. Xu, and J. Tang.  
Contextual residual aggregation for ultra high-resolution image inpainting.  
In \textit{CVPR}, pages 7508--7517, 2020.

\bibitem{liu2022structure}
Y. Liu, S. Wang, Y. Xu, J. Tang, and B. Li.  
Structure-aware image inpainting with multi-scale gated convolutions.  
In \textit{CVPR}, pages 2756--2765, 2022.

\bibitem{zeng2020learning}
Y. Zeng, J. Fu, H. Chao, and Y. Zheng.  
Learning pyramid-structure attention for image inpainting.  
In \textit{ECCV}, pages 481--497, 2020.

\bibitem{li2020recurrent}
Y. Li, S. Liu, J. Yang, and M.-H. Yang.  
Recurrent feature reasoning for image inpainting.  
In \textit{CVPR}, pages 7760--7768, 2020.

\bibitem{wan2021image}
R. Wan, Y. Zhang, Z. Li, Y. Wang, and L. Ma.  
Image inpainting via learning contextual residual aggregation.  
In \textit{CVPR}, pages 8281--8290, 2021.

\bibitem{lugmayr2022repaint}
A. Lugmayr, M. Danelljan, and R. Timofte.  
RePaint: Inpainting using denoising diffusion probabilistic models.  
\textit{arXiv preprint arXiv:2201.09865}, 2022.

\bibitem{liu2021pd}
H. Liu, X. Zhang, Y. Wan, and D. Lin.  
PD-GAN: Probabilistic diverse GAN for image inpainting.  
In \textit{CVPR}, pages 9371–9381, 2021.

\bibitem{shao2021generative}
H. Shao, Y. Wang, Y. Fu, and Z. Yin.  
Generative image inpainting via edge structure and color aware fusion.  
\textit{Journal of Visual Communication and Image Representation}, 2021.

\bibitem{places2}
\url{https://www.kaggle.com/datasets/nickj26/places2-mit-dataset}

\bibitem{masks}
\url{https://github.com/karfly/qd-imd}

\end{thebibliography}
